A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-15 manuscript.Rmd
add newline after header
fix figure ref

```{r, results='asis', echo=FALSE}
# in case we want to reuse this example later
markdown_example <- "
<!--this is a Markdown file -->
# Header
Normal text.
Important **word**.

@@

This will create a file with the name `README.Rmd`.
When you knit this file, it in turn creates a `README.md`.
That means you can include R code or plots etc. within the readme.
The `README.md` file will look pleasant in the browser, just like in Figure \@ref(fig:idea-change).

>>>>

```{r, results='asis', echo=FALSE}
# in case we want to reuse this example later
markdown_example <- "
<!--this is a Markdown file -->
# Header

Normal text.
Important **word**.

@@

This will create a file with the name `README.Rmd`.
When you knit this file, it in turn creates a `README.md`.
That means you can include R code or plots etc. within the readme.
The `README.md` file will look pleasant in the browser, just like in Figure \@ref(fig:readme).
